%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume
\documentclass[margin,line]{resume}
%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Dhruv Agrawal}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    Senior Year Undergraduate Student \hfill webpage: http://dhruvjain.info \vspace{0mm}\\\vspace{0mm}%
    Indian Institute of Technology \hfill e-mail: dhruv-ee@student.iitd.ac.in\vspace{0mm}\\\vspace{-4.5mm}%
    New Delhi, India		   \hfill date of birth: January, 7 '1991 \vspace{0mm}\\\vspace{1.5mm}% 

    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
    Computer Vision, Machine Learning, Robotics \vspace{2mm}

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
    
    \begin{tabular}{c c c c}
    \textbf{Year} & \textbf{Degree/Exam} & \textbf{Institute} & \textbf{GPA/Marks} \\
    --- & B.Tech Electrical Engg. & Indian Institute of Technology Delhi & \textbf{7.38/10.0} \\
    2009 & High School CBSE & DAV Public School Kota & 89.8\% \\
    2007 & Senior School CBSE & Maharana Mewar Public School Udaipur & 95.8\%
    %\textsl{B.Tech in Computer Science and Engineering} \hfill \textbf{ July 2009 -- present}\vspace{-3mm}\\\vspace{-1mm}%
	
    \end{tabular}	\vspace{1mm}
    
%     Delhi Public School, Mathura Road Delhi, India \vspace{2mm}% 
%      \begin{list2}
%         \item High School, AISSCE, \textbf{Aggregate Marks: 93.8\%} 		\hfill \textbf{2009}\vspace{-3mm}\\\vspace{-1mm}% Aggregate Marks: 93.8\%	
%     \end{list2}\vspace{-1mm}
%       
%     \begin{list2}
%         \item Senior School, AISSE, \textbf{Aggregate Marks: 95.2\%}		 \hfill \textbf{2007}\vspace{-3mm}\\\vspace{-1mm}%
%     \end{list2}\vspace{-1mm}

    %__________________________________________________________________________________________________________________
    % Acheivements
    \section{\mysidestyle  Selected\\Publications}
    Abstract ID- 392, Abstract Title- \textbf{``Design and User-Study of an affordable Indoor Navigation System for Visually Impaired''}, accepted for presentation in 13th International Conference on ``Mobility and Transport for Elderly and Disabled People'' \textbf{TRANSED 2012}
    \section{\mysidestyle Scholastic \\Acheivements} 
    \begin{list2} 
	\setlength{\itemindent}{-0.63em} 
	\item Summer Undergraduate Research Award 2011, a research project \textbf{funded by the Ministry of \\
\hspace*{-3.5mm} HRD, India} for project on FPGA acceleration of sequence alignment algorithms.%
	\item IITD Semester Merit Award for being in top 7\% of all the undergraduate 2009 batch students.%
	\item All India Rank 1(PD) in IIT JEE and AIEEE 2009.
    \end{list2}		\vspace{2mm}
    %__________________________________________________________________________________________________________________
    % Projects
    \section{\mysidestyle Projects}

    \textbf{INDOOR NAVIGATION SYSTEM FOR VISUALLY IMPAIRED}			\vspace{1mm}\\\vspace{1mm}% 		        
    (Prof. M. Balakrishnan, Prof. P.V.M. Rao)					\\\vspace{1mm}%
    \textsl{Embedded Systems, Assistive Technology}          		        \hfill(May, 2011 -- April, 2012) \\
    Low-cost \textbf{($<$ INR 800)} setup to help a visually impaired individual navigate freely inside a building via acoustic messages from mobile phone. The Infrared based system requires mimimal additional building infrastructure and a small user waist-worn device.    \hfill \textsl{(www.roshni.info)}
    \begin{list2}
     \item Surveyed and tested different technologies for localization(RSSI, RFID, Ultrasound, Infrared) 
     \item Developed the waist-worn device consisting of accelerometer, Infrared and bluetooth modules which communicates with hand-held android phone application 
     \item Developed the wall mounted network with IRs, microcontrollers and buzzers
     \item \textbf{Demonstrated in an institute building during IIT Delhi - Open House '2012.\\ Received considerable media attention}
     \item \textbf{Field testing with 5 visually impaired users} gave a positive and encouraging feedback 
    \end{list2}
			      \vspace{1mm}

    \textbf{WHITESPACE NETWORK FOR VIDEO UPLINK FROM VEHICULAR SYSTEMS}    \vspace{1mm}\\\vspace{1mm}%
    (Prof. Vinay Ribeiro, Prof. Manish Sharma)					\\\vspace{1mm}%
    \textsl{Computer Networks}                                  		\hfill(July, 2011 -- April, 2012) \\%	
    This is a joint project of IIT Delhi and Univ. of Wisconsin, Madison. It aims to send video surveillance information collected through a network of city buses to a central location via the cognitive radio technology. I worked on the simulation and implementation of MAC-layer protocol.
    \begin{list2}
        \item Explored wireless technologies(WiFi, WiMAX, GSM, CDMA) to choose the appropriate one
        \item \textbf{Designed the complete physical layout of the APs and the MAC-Layer} based on two different technologies: Distributed polling with RSSI based localisation and TDMA with GPS
	\item Lab tested polling and handoff mechanisms on USRP2 boards using GNU Radio software suit
     \end{list2}	
			      \vspace{-1mm}
    \textbf{\textsl{Research Assistantship}} 	 			\hfill\textbf{Univerisity of Wisconsin, Madison}\\%	
    (Prof. Suman Banerjee)						\hfill(May, 2011 -- Present) \\
    Working on modifying OFDM design of Rice Univerisity's WARP board to achieve shrinkage of the default bandwidth by disabling subcarriers.

    
    \textbf{FPGA AS ACCELERATORS FOR NEXT GENERATION SEQUENCING}  		\vspace{1mm}\\\vspace{1mm}%
    (Prof. M. Balakrishnan)							\\\vspace{1mm}%
    \textsl{Embedded Systems, Computational Biology}   		                 \hfill(Mar, 2011 -- Feb, 2012) \\
    Hardware-Software co-design for Bioinformatics applications to              \hfill \textsl{(www.seq-align-fpga.info)} \\
    explore FPGAs for speeding up DNA sequence alignment algorithms.              
    \begin{list2}
        \item Surveyed and selected some of the best known algorithms(BWA, MAQ, SOAP etc.)
	\item Profiled the software-tools in terms of usage and running time and noted their critical areas 
	\item Selected one algorithm and designed the modules for its parallelized implementation on FPGA
    \end{list2}    	

    \textbf{Course Projects --}
    \begin{list2}
         \item \textbf{Multiplayer Ping Pong Game} (Networking) (July, 2010 - Nov, 2010) : Multiplayer networking game supporting
upto four players. Game was coded in C++ using OpenGL. Only submission which used UDP broadcasting for the clients to automatically search for the available servers
         \item \textbf{MIPS-32 Processor Design} (Computer Architecture) (July, 2010 - Nov, 2010) : Designed a subset of MIPS-32 instruction set on a simulator. The application computes and displays the day of the week corresponding to the
specified date
        \item \textbf{Implementation of Systolic Sorting Architecture on FPGA Board} (Embedded Systems) (Jan, 2011 - Apr,
2011) : Implemented sorting of numbers on FPGA board via the systolic array of Digital Processing Units (DPUs)
Code was written in VHDL
        \item \textbf{Android Application for GPS Navigation} (Design Practices) (July, 2010 - Nov, 2010) : An android application in Java and Web
interface in PHP, Javascript, Jquery and Ajax for finding the shortest path from one point to another based on
current traffic density
        \item \textbf{Interpreters for subsets of Prolog and SML} (Programming Languages) (Jan - Apr, 2011) : Built a
lexer, parser and an interpreter for a subset of the functions provided by SML and prolog
	\item \textbf{Sorting Algorithms -CatapultC} (System Level Design and Modellling) (Jan - Apr, 2012) : Explored the performance of various sorting algorithms on HLL Design tool - CatapultC 
	\item \textbf{Enhanced Pintos Operating System} (Opeating Systems) (Jan - Apr, 2013): Coded the relevant parts of basic inefficient Pintos OS to make it more reliable and improve performance
	\item \textbf{New Algorithm for Gene Prediction} (Bioinformatics)  (Jan - March, 2013): Developed a faster and more reliable algorithm for Human Gene Prediction based on existing softwares.
  \end{list2}

    \textbf{Independent Projects --}
    \begin{list2}	
	\item \textbf{Animation Clip display} (Embedded Systems) (Nov, 2010 - Jan, 2011) : Created a  colour-encrypted anitmation clip on VGA screen from a sequence of images using FPGA board
	\item \textbf{Rationality in Decision Making} (Social Psychology) (July, 2011 - Nov, 2011) : To explore whether human beings are rational in their approach of making decisions and how their rationality is influenced by social factors like ambitions and moral values
    \end{list2}		\vspace{2mm}
   
     % Relevant Courses
    \section{\mysidestyle Relevant Courses}
    \begin{tabular}{l l l}
    System Level Design and Modelling&Operating Systems&Computer Aided Design\\Digital Hardware Design&Bioinformatics&Computer Networks\\Embedded System Design Lab&Signals and Systems&Computer Architecture\\Analysis and Design of Algorithms&Digital Electronics&Programming Languages

    \end{tabular}	\vspace{1mm}
    %__________________________________________________________________________________________________________________
 
     %__________________________________________________________________________________________________________________
    % POR
    \section{\mysidestyle Position of \\Responsibility}
    \begin{list2}
      \setlength{\itemindent}{-0.63em}
	\item Served as a \textbf{volunteer for International Conference on Field Programmable Technology}\\
	\hspace*{-3.3mm} held in New Delhi, India. Successfully organised the FPGA design competition ``Connect6''.%
	\item Served as a \textbf{Student Mentor} for the CSE Department First Year Students. Helped 
	them get 
	\hspace*{-3.3mm} acquainted with the college studies and environment.
      \end{list2}		\vspace{1mm}
 %__________________________________________________________________________________________________________________
 



    %__________________________________________________________________________________________________________________
    % Other Activities
    \section{\mysidestyle Other \\Activities}
    \begin{list2}
      \setlength{\itemindent}{-0.63em}
	\item Attended the summer camp on Information Retrieval and Web Search by Yahoo in Bangalore.%
	\item Active member of Topcoder Programming Community with the current rating of 1496(Blue Coder).%
	\item Went for a rural group exposure with a team of 12 students as part of an NGO programme(Pravah).%
	\item Built websites for Startups: ``Goshti'' and ``thewittyshit'' and developed facebook applications.%
    \end{list2}		\vspace{1mm}
    %__________________________________________________________________________________________________________________
 
    
    % Computer Skills
    \section{\mysidestyle Programming \\Languages} 
    VHDL, Java, C/C++, Python, SML, Lex, Yacc, Prolog, PHP, Javascript/Jquery, Ajax, MySQL, ASP.NET, HTML/CSS, Bash, \LaTeXe, Assembly Language, FBML/FBJS, SystemC, Bluespec

    \section{\mysidestyle Softwares} 
    Xilinx ISE, Xilinx Platform Studio, Eclipse/Android, Netbeans, Jcreator, MS Visual Studio, Matlab, Drupal, Wordpress, Joomla, Ideas, SolidWorks, GNU Radio, Mentor Graphics CatapultC, Intel Vtune

    \section{\mysidestyle Hardwares}
    FPGAs(Virtex, Spartan), Microcontrollers(Arduino/Atmega, PIC), PCB Design(Diptrace/Eagle), WARP, USRP, Xilinx Zynq EPP, Alpha Data

    \section{\mysidestyle Interests}
    Web-Development, Swimming, Humanistic Psychology, Musical Instrument- Keyboard	\vspace{1.5mm}
    %__________________________________________________________________________________________________________________
    % Referees
    %______________________________________________________________________________________________________________________
    \section{\mysidestyle Referees}
    %{\sl Available on request.}
    \begin{tabular}{@{}p{8.3cm}p{8.3cm}}%p{5cm}}
    \textbf{Prof. M. Balakrishnan} 		   & \textbf{Prof. Vinay Joseph Ribeiro}       \\%&  \textbf{Prof. Manish Sharma}         \\
    Professor and Deputy Director of Faculty 	   &  Assistant Professor                      \\%&  Associate Professor			\\                                     
    Indian Institute of Technology                 &  Indian Institute of Technology           \\%&  Indian Institute of Technology	\\
    New Delhi, India			           &  New Delhi, India        		       \\%&  New Delhi, India			\\
    mbala@cse.iitd.ernet.in                        &  vinay@cse.iitd.ernet.in	           	     
    %http://cse.iitd.ac.in/\texttt{\char`\~}mbala        &  http://cse.iitd.ac.in/\texttt{\char`\~}vinay       &  http://care.iitd.ac.in/\texttt{\char`\~}manish       \\
    \end{tabular}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}
%______________________________________________________________________________________________________________________
% EOF